---
title: "musings on R Markdown and how I’ll use it"
author: "W. McDonald"
date: "7/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Write a Book on Neuropathology

Copy and paste from prior book draft... figure out tables


```{r cars}
summary(cars)
```

## Spiffy Plot

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

**Note** that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Make sure to comment out your code, but what role comments in RMD documents?

Still figuring out this GIT stuff in RStudio.

More to come.

Hey, should I write the GATA3 paper in RMD? Small changes are not worth committing, since a committed document is the "gold standard," the "display copy," if you like. Nonetheless, the habit of committing is important. 

Why use the git interface in RStudio rather than the terminal in RStudio? Doesn't seem to add much, and it keeps me slightly further from git...

```{r message=FALSE, warning=FALSE}
library(tidyverse)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```
